Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-fm.tex

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}.

>>>>

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}.
=======
% Bitoun2005 -> PMID: 16227997; Zuechner2005 -> PMID: 15731758; Ali2019 -> PMID: 31017801
% Added: Ali2019 -> ich suche noch nach weiteren Beispielen

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating 
the dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 
cells (figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent 
nanoparticles in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells 
\cite{Kemp2008} and for investigating the differentiation of stem cells \cite{Gorelik2008}. 
Furthermore, it has been utilized in studies investigating endocytotic pathways 
\cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and \cite{Shevchuk2012,Ali2019}. In the study of 
Shevchuk et al. \cite{Shevchuk2012} in 2012 an alternative closing mechanism for clathrin-coated 
pits (CCPs) were found by recording topography simultaneously with the fluorescence of actin-
binding protein-green fluorescent protein (Abp1-GFP) and clathrin light-chain-enhanced green 
fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}. In the study of Ali et al. \cite{Ali2019} the 
effect of mutations in the Dynamin 2 (DNM2) gene, which play a role in diseases like centronuclear 
myopathy \cite{Bitoun2005} or Charcot-Marie-Tooth disease \cite{Zuechner2005}, on the morphology 
and the kinetics of the uptake-relevant processes -- formation, internalization … -- of CCPs were
investigated.

In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized 
human alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}. 
>>>>>>> 1dc5732e20282e8a916a002a11827856299c8360
